Penalized regression for left-truncated and right-censored survival data

### 2021-01-11 manuscript.tex
add acknowledgments, data availability statement

\pdfbookmark[1]{References}{References}
\bibliography{references}

>>>>

\section*{Acknowledgments} 
We thank T. Hastie and K. Tay for their work in implementing left truncation-adjusted Cox models in \pkg{glmnet}.

\section*{Data availability statement}
The data that support the findings of this study have been originated by Flatiron Health, Inc. and Foundation Medicine, Inc. These de-identified data may be made available upon request, and are subject to a license agreement with Flatiron Health and Foundation Medicine; interested researchers should contact <cgdb-fmi@flatiron.com> to determine licensing terms.

Code used to produce the analysis is publicly available at https://github.com/phcanalytics/coxnet-ltrc.

%\section*{References} 
%\pdfbookmark[3]{References}{References}
\bibliography{references}
